\documentclass{beamer}
\usepackage{float}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{rotating}
\hypersetup{colorlinks=true}
\usetheme{rob}
%\usetheme{Boadilla}
%\useinnertheme{circles}
%\useoutertheme{infolines}
%\usecolortheme{whale}

\title[G4DMC]{Excessive Phonon Energy in G4DMC Events}
\author{Rob Agnese}
\institute{University of Florida}
\date{February 27, 2017}

\begin{document}

\begin{frame}[plain, noframenumbering]
    \titlepage{}
\end{frame}

\begin{frame}{The Problem}
    \vfill
    While debugging the track weighting discrepencies, I noticed that
    even without downsampling, we were getting too much energy out from a 
    simulation. \\

    For an electron recoil we should expect:
    \begin{equation}
        E_{phonon} = E_{recoil} + 4 \textrm{volt} \times 
        \textrm{floor}\left(\frac{E_{recoil}}{E_{pair}}\right)
    \end{equation}

    For the 1 keV event I tested, that should be $\sim$ 2.4 keV. G4DMC collected
    a total of $\sim$ 3.1 keV of phonon energy.
    \vfill
\end{frame}

\begin{frame}{Investigation}
    \vfill
    Some immediate consistency checks:
    \begin{itemize}
        \item Charge drift speeds still match data.
        \item Energy partitioner creates correct initial tracks (energies sum to $E_{recoil}$).
        \item Luke phonon emissions conserve energy on case-by-case basis.
    \end{itemize}
    \vfill
\end{frame}

\begin{frame}{Tests}
    \vfill
    We have checked several potential sources of error:
    \begin{itemize}
        \item Use uniform electric field instead of COMSOL field - \textbf{no change}.
        \item Turn off inter-valley scattering (known to be non-physical) - \textbf{no change}.
        \item Create only phonons - \textbf{Correct energy output}!
        \item Shoot exactly one charge carrier pair - \textbf{Excess still present}.
    \end{itemize}
    \vfill
\end{frame}

\begin{frame}{Places Left to Look}
    \vfill
    The bug must be in the charge physics. We've ruled out inter-valley scattering
    and Luke phonon emission. The drift curves also should rule out E-field
    acceleration bugs. There are three processes left:
    \begin{itemize}
        \item DriftBoundaryProcess - When a charge carrier is absorbed, releases
            its kinetic energy as phonons.
        \item DriftRecombinationProcess - When a charge carrier comes to rest
            in the crystal, it is killed and releases half of the gap energy
            as phonons.
        \item EnergyLimiter - When any particle is below its energy threshold,
            it is simply killed and deposits its kinetic energy as NIEL. This
            shouldn't be triggering ever for charge carriers as threshold = 0.
    \end{itemize}
    \vfill
\end{frame}

\end{document}
